Model to study co-evolution of trade an culture

### 2015-03-27 article.tex

\simon{reference to the R package and the theoreticla ref in the Rpackage?}
Those distribution exhibit power law like attribute and we can fit them. The result of the alpha fitted with are in the table \ref{tab:mualpha}. The alpha values represent the mean of the fitted alpha for each run computed using RPACKAGE with the standard deviation associated with each mean.
\begin{figure}[hbp]
	\begin{center}
%		\includegraphics[width=7cm]{img/allmuRandMaxBentleyValues.pdf}
	\end{center}
	\caption{rand()\%RAND\_MAX}
	\label{fig:allMutation}
\end{figure}

>>>>

\simon{reference to the R package and the theoretical ref in the Rpackage?}
Those distribution exhibit power law like distribution in such a way that we can find a power law $formul powerlaw$ that can fit it. The value of the $\alpha$ parameter of the fitted power law are in the table \ref{tab:mualpha}. Those $\alpha$ values are the mean of the $\alpha$ parameter of each power law fitted to each run and computed using with the standard deviation associated with each mean.PACKAGE. The SD are the SD associated each means .
\begin{figure}[hbp]
	\begin{center}
%		\includegraphics[width=7cm]{img/allmuRandMaxBentleyValues.pdf}
	\end{center}
	\caption{Distribution of frequencies depending on the $\mu$ parameter}
	\label{fig:allMutation}
\end{figure}
